---
title: "Buy Online Pick Up in Store (BOPS)"
author: "Kevin, Ram, Ryo"
date: "June 6, 2017"
output: 
  slidy_presentation: default
  ioslides_presentation: default
---

```{r echo=FALSE, warning=FALSE, message=FALSE}
setwd("C:/Users/ktseng/Dropbox/SCU/OMIS 3392/project") 
# Assessing the impact of buy-online-pick up-in store strategy on online and Brick-and-mortar store sales and returns
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
## Load Data Set
library(data.table)
library(readr)
library(dplyr)
library(VIF)
library(usdm)
library(AER)
library(foreign)
bops <- read_csv("C:/Users/ktseng/Dropbox/SCU/OMIS 3392/project/data.txt")
bops <- as.data.table(bops)
bops2012 <- fread("C:/Users/ktseng/Dropbox/SCU/OMIS 3392/project/BOPS-FY12.csv")
bops2013 <- fread("C:/Users/ktseng/Dropbox/SCU/OMIS 3392/project/BOPS-FY13.csv")

# bops - original data file
# bops1 - used for returns model
# bops2 - used for sales model
# bops3 - sales model for store 2 and 6
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
bops$gender[is.na(bops$gender)] <- "U"
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
bops$homeowner_code[bops$homeowner_code == "R"] <- 0
bops$homeowner_code[bops$homeowner_code == "O"] <- 1
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
bops$store_number <- as.factor(bops$store_number)
bops <- within(bops, store_number <- relevel(store_number, ref = 3))
```


```{r echo=FALSE, warning=FALSE, message=FALSE}
# Multiple plot function
#
# ggplot objects can be passed in ..., or to plotlist (as a list of ggplot objects)
# - cols:   Number of columns in layout
# - layout: A matrix specifying the layout. If present, 'cols' is ignored.
#
# If the layout is something like matrix(c(1,2,3,3), nrow=2, byrow=TRUE),
# then plot 1 will go in the upper left, 2 will go in the upper right, and
# 3 will go all the way across the bottom.
#
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)

  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }

 if (numPlots==1) {
    print(plots[[1]])

  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}
```


# Visualization of Variables
```{r echo=FALSE, warning=FALSE, message=FALSE}
## Normality Check
library(ggplot2)
p1 <- ggplot(bops, aes(x=net_purchase_amount)) + 
  geom_histogram()
p2 <- ggplot(bops, aes(x=age_band))+
  geom_histogram()
p3 <-ggplot(bops, aes(x=est_income_code))+
  geom_histogram()
p4 <-ggplot(bops, aes(x=length_of_residence))+
  geom_histogram()
p8 <-ggplot(bops, aes(x=summary))+
  geom_bar()
p9 <-ggplot(bops, aes(x=child))+
  geom_bar(width=0.3)
p10 <-ggplot(bops, aes(x=homeowner_code))+
  geom_bar(width=0.3)
p11 <-ggplot(bops, aes(x=ethnic_code))+
  geom_bar(width=0.3)
p12 <-ggplot(bops, aes(x=year)) +
  geom_bar(width=0.3)
multiplot(p1, p2, p3,p4,p8, p9, p10, p11, p12, cols=3)

```


# Goal 1: Store Sales

**Purpose**:  Assess the impact of the BOPS strategy on store sales  

**Primary Independent Variable**: BOPS (dummy variable)  
0 - mail  
1 - store pickup

**Secondary Independent Variable**: Store Number  
As the purpose states, we want to assess impact at the store level.

**Control Variables**:  
log(net_puchase_amount)*  
gender  
age_band  
est_income_code  
ethnic_code  

**Dependent Variable**: Transaction Count (generated variable)  
* Why is net_purchase_amount not a sufficient dependent variable?  
Will look at the program 1 year before and 1 year after the start.

**Unused Variables**:  
transaction_id  
customer_id  
purchase_date  
sku  
return_date  
return_store  
time_to_return  
homeowner_code  
length_of_residence  
child  
year  
month_index  
summary  



# Data Cleaning for sales model

## Create BOPS dummy variable
Data was originaly given in two seperate files and so we have to merge them.  
0 = Purchase in store  
1 = Purchase online  
```{r echo=FALSE, warning=FALSE, message=FALSE}
# Add column to the individual years
bops2012 <- bops2012[,-c(1,3)]
bops2012 <- cbind(bops2012, b2012 = 1)
bops2013 <- bops2013[,-c(1,3)]
bops2013 <- cbind(bops2013, b2013 = 1)

# Merge dataframes
bops <- merge(bops, bops2012, by="transaction_id", all.x=TRUE)
bops <- merge(bops, bops2013, by="transaction_id", all.x=TRUE)

# fill in NA
bops$b2012[is.na(bops$b2012)] <- 0
bops$b2013[is.na(bops$b2013)] <- 0

#merge the 2 columns
bops$bops <- bops$b2012 + bops$b2013
bops$gender <- as.factor(bops$gender)
bops$ethnic_code <- as.factor(bops$ethnic_code)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
bops2 <- bops[,-c(3,6:10,18:19, 22:23)]
```

## Filter out customers with only 1 transaction
We are primarily concerned with return customers and not one time only customers.
```{r echo=FALSE, warning=FALSE, message=FALSE}
bops2$customer_id <- as.factor(bops2$customer_id)
bops2a <- bops2[which(bops2$month_index <= 24),]
bops2b <- bops2[which(bops2$month_index <= 36 & bops2$month_index >= 25),]
# determine duplicates
a = count(bops2a, customer_id)
bops2a <- merge(bops2a, a, by="customer_id", all.x=TRUE)
bops2a <- bops2a[which(bops2a$n >= 2),]
bops2a <- bops2a %>%
  group_by(customer_id) %>%
  summarise(net_purchase_amount = sum(net_purchase_amount), store_number = first(store_number), gender = first(gender), age_band = first(age_band), est_income_code = first(est_income_code), ethnic_code = first(ethnic_code), bops = first(bops), numitems = first(n), homeowner_code = first(homeowner_code), length_of_residence = first(length_of_residence), child = first(child))
a = count(bops2b, customer_id)
bops2b <- merge(bops2b, a, by="customer_id", all.x=TRUE)
bops2b <- bops2b[which(bops2b$n >= 2),]
bops2b <- bops2b %>%
  group_by(customer_id) %>%
  summarise(net_purchase_amount = sum(net_purchase_amount), store_number = first(store_number), gender = first(gender), age_band = first(age_band), est_income_code = first(est_income_code), ethnic_code = first(ethnic_code), bops = first(bops), numitems = first(n), homeowner_code = first(homeowner_code), length_of_residence = first(length_of_residence), child = first(child))
bops2 <- rbind(bops2a, bops2b)
cat("From our original set of", nrow(bops), "data points, we are left with", nrow(bops2), "data points.")
```



## Data points that are missing information
```{r echo=FALSE, warning=FALSE, message=FALSE}
bops2$missing_data <- 0
bops2$missing_data <- rowSums(is.na(bops2))
table(bops2$missing_data)
```
Confirm that we will not lose too much data due to NA.


## net_purchase_amount (log)
```{r echo=FALSE, warning=FALSE, message=FALSE}
cat("Number of na entries:", sum(is.na(bops$net_purchase_amount)))
bops2$net_purchase_amount <- log(bops2$net_purchase_amount+1)
p1 <- ggplot(bops, aes(x=net_purchase_amount)) + 
  geom_histogram()
p2 <- ggplot(bops2, aes(x=net_purchase_amount))+
  geom_histogram()
multiplot(p1, p2, cols=2)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
bops3 <- bops2[!(bops2$store_number == "5998"),]
bops3 <- within(bops3, store_number <- relevel(store_number, ref = 3))
```


# Sales Model 1 OLS (2+ items purchased)
```{r echo=FALSE, warning=FALSE, message=FALSE}
sales1 <- lm(numitems ~ bops + store_number + net_purchase_amount + gender + age_band + est_income_code + ethnic_code, data=bops3)
summary(sales1)
```

# Sales Model with Interaction (2+ items purchased)
We want to see the effect on stores.
```{r echo=FALSE, warning=FALSE, message=FALSE}
sales2 <- lm(numitems ~ bops * store_number + net_purchase_amount + gender + age_band + est_income_code + ethnic_code, data=bops3)
summary(sales2)
```

## Comparison of the two models (nested)
```{r echo=FALSE, warning=FALSE, message=FALSE}
anova(sales1, sales2, test="Chisq")
```

# Poisson

```{r echo=FALSE, warning=FALSE, message=FALSE}
poisson1 <- glm(numitems ~ bops * store_number + net_purchase_amount + gender + age_band + est_income_code + ethnic_code, family="poisson", data=bops3)
summary(poisson1)
```

## Heteroscedasticity test and IRRs
```{r echo=FALSE, warning=FALSE, message=FALSE}
library(lmtest)
gqtest(poisson1) 
bptest(poisson1) 
```

Both tests are significant therefore we have heteroscedasticity.

## Huber-White robust standard errors
```{r echo=FALSE, warning=FALSE, message=FALSE}
f <- as.data.frame(coeftest(poisson1, vcov = vcovHC(poisson1, "HC1"))[,-c(2,3)])
f <- cbind(summary(poisson1)$coefficients[,-c(2,3)], f)
colnames(f) <- c("Orig Est", "Pr(>|z|)", "Std Errors Est", "Pr(>|z|)")
f[,2][f[,2] <= 0.05] <- "***"
f[,2][f[,2] >= 0.05] <- ""
f[,4][f[,4] <= 0.05] <- "***"
f[,4][f[,4] >= 0.05] <- ""
f
```

bops and store number are still significant.

```{r echo=FALSE, warning=FALSE, message=FALSE}
exp(coef(poisson1)) # We see that the incident rate for facebookvisit is 1.083 times the incident rate for the no facebookvisit. Customers who visit Facebook before Amazon purchase 8.3% more than customers who visit Amazon.com directly.
```

## Model fit test
```{r echo=FALSE, warning=FALSE, message=FALSE}
cat("Chi-squared test statistic:", with(poisson1, null.deviance - deviance))
cat("Degrees of freedom:", with(poisson1, df.null - df.residual))
cat("P value:", with(poisson1, pchisq(null.deviance - deviance, df.null - df.residual, lower.tail = FALSE)))
```
Horrible fit

# Negative Binomial model
```{r echo=FALSE, warning=FALSE, message=FALSE}
library(foreign)
library(MASS)
summary(negbin1 <- glm.nb(numitems ~ bops * store_number + net_purchase_amount + gender + age_band + est_income_code + ethnic_code, data = bops3))
```

## Heteroscedasticity
```{r echo=FALSE, warning=FALSE, message=FALSE}
gqtest(negbin1) 
bptest(negbin1)
e <- as.data.frame(coeftest(negbin1, vcov = vcovHC(negbin1, "HC1"))[,-c(2,3)])
e <- cbind(summary(negbin1)$coefficients[,-c(2,3)], e)
colnames(e) <- c("Orig Est", "Pr(>|z|)", "Std Errors Est", "Pr(>|z|)")
e[,2][e[,2] <= 0.05] <- "***"
e[,2][e[,2] >= 0.05] <- ""
e[,4][e[,4] <= 0.05] <- "***"
e[,4][e[,4] >= 0.05] <- ""
e
```

## Test model fit
```{r echo=FALSE, warning=FALSE, message=FALSE}
cat("Chi-squared test statistic:", with(negbin1, null.deviance - deviance))
cat("Degrees of freedom:", with(negbin1, df.null - df.residual))
cat("P value:", with(negbin1, pchisq(null.deviance - deviance, df.null - df.residual, lower.tail = FALSE)))
```
Model fits the data since the test is significant

## Compare Poisson regression to Negative Binomial regression
Chisq Test  
```{r echo=FALSE, warning=FALSE, message=FALSE}
X2 <- 2 * (logLik(negbin1) - logLik(poisson1))
X2
pchisq(X2, df = 1, lower.tail=FALSE) 
```
Negative Binomial is more appropriate than Poisson since there is over-dispersion.  


# Sales Model Summary
Final Model: Negative Binomial
numitems ~ bops * store_number + net_purchase_amount + gender + age_band + est_income_code + ethnic_code  



```{r echo=FALSE, warning=FALSE, message=FALSE}
library(effects)
plot(effect(term="bops:store_number", mod=negbin1, default.levels=2),multiline=TRUE)
```

```{r echo=FALSE, warning=FALSE, message=FALSE, results = 'asis'}
library(knitr)
z <- matrix(c("$170", "$146", "75,000", "6,500", "1.5", "0.6", "$19,125,000", "$569,400"), ncol=4)
colnames(z) <- c("Mean Transaction Price", "Number of Customer", "Transaction Increase", "Total Sales Increase")
rownames(z) <- c(2, 6)
kable(z, caption = "Sales Increase")
```



# Goal 2: Store Returns

**Purpose**:  Assess the impact of the BOPS strategy on store returns  

**Dependent Variable**: return (dummy variable)  
0 - Item has not been returned  
1 - Item has been returned  

**Primary Independent Variable**: BOPS (dummy variable)  
0 - mail  
1 - store pickup

**Secondary Independent Variable**: Store Number  
As the purpose states, we want to assess impact at the store level.

**Control Variables**:  
log(net_puchase_amount)  
gender  
age_band  
est_income_code  
ethnic_code  
month  
summary *

# Data Cleaning for returns model

## Data points that are missing information
```{r echo=FALSE, warning=FALSE, message=FALSE}
bops1 <- bops[,-c(3, 6, 8:10, 20, 22:23)]
bops1$missing_data <- 0
bops1$missing_data <- rowSums(is.na(bops1))
table(bops1$missing_data)
```


## net_purchase_amount (log)
```{r echo=FALSE, warning=FALSE, message=FALSE}
library(ggplot2)
cat("Number of na entries:", sum(is.na(bops$net_purchase_amount)))
bops1$net_purchase_amount <- log(bops1$net_purchase_amount+1)
p1 <- ggplot(bops, aes(x=net_purchase_amount)) + 
  geom_histogram()
p2 <- ggplot(bops1, aes(x=net_purchase_amount))+
  geom_histogram()
multiplot(p1, p2, cols=2)
```


```{r echo=FALSE, warning=FALSE, message=FALSE}
returns1 <- bops1
returns1$summary <- as.factor(returns1$summary)
```

# Returns Model 1 OLS
```{r echo=FALSE, warning=FALSE, message=FALSE}
retmodel1 <- lm(return ~ bops + store_number + net_purchase_amount + gender + age_band + est_income_code + ethnic_code + month + summary, data=returns1)
summary(retmodel1)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
#dfret1=data.frame(returns1$bops,returns1$net_purchase_amount,returns1$age_band,returns1$est_income_code)
#vif(dfret1)
```

# Returns Model 2 OLS (interaction with store_number)
```{r echo=FALSE, warning=FALSE, message=FALSE}
retmodel2 <- lm(return ~ bops * store_number + net_purchase_amount + gender + age_band + est_income_code + ethnic_code + month+ summary, data=returns1)
summary(retmodel2)
```

## Comparison of models
```{r echo=FALSE, warning=FALSE, message=FALSE}
anova(retmodel1,retmodel2,test="Chisq")
```
Model with interaction variable is better

## Range of Returns Model 2
```{r echo=FALSE, warning=FALSE, message=FALSE}
predictedprobability_lm<-predict(retmodel2)
#Range along is sufficient to explain why we have to switch to Logit model.
range(predictedprobability_lm)
library(aod)
library(Rcpp)
```

We expect the results to be between 0 and 1.  However it is out of bounds.

#Logit Model 

## Satisfaction of Logit Requirements
```{r echo=FALSE, warning=FALSE, message=FALSE}
table(returns1$return)
```

## Model
```{r echo=FALSE, warning=FALSE, message=FALSE}
returns1$gender <- as.factor(returns1$gender)
returns1$ethnic_code <- as.factor(returns1$ethnic_code)
returns1$month <- as.factor(returns1$month)
logit1<- glm(return ~ bops * store_number + net_purchase_amount + gender + age_band + est_income_code + ethnic_code + month+ summary, data=returns1, family="binomial")
summary(logit1)
```


# Marginal Effect
```{r echo=FALSE, warning=FALSE, message=FALSE}
library(mfx)
#Rule of thumb, we always assume heterskedasticity is present, thus we use robust standard error to adjust standard errors for independent variables.
b <- logitmfx(formula=return ~ bops * store_number + net_purchase_amount + gender + age_band + est_income_code + ethnic_code + month+ summary, data=returns1, robust=TRUE)
b
```

#Comparison with Probit model (marginal effects)
```{r echo=FALSE, warning=FALSE, message=FALSE}
probit1<- glm(return ~ bops * store_number + net_purchase_amount + gender + age_band + est_income_code + ethnic_code + month+ summary, data=returns1, family=binomial(link="probit"))
c <- probitmfx(formula=return ~ bops * store_number + net_purchase_amount + gender + age_band + est_income_code + ethnic_code + month+ summary, data=returns1, robust=TRUE)
a <- as.data.frame(b$mfxest[,1])
a <- cbind(a, c$mfxest[,1])
colnames(a) <- c("logit", "probit")
a
```

# Endogenity
```{r echo=FALSE, warning=FALSE, message=FALSE}
returns1$child <- as.numeric(returns1$child)
returns1$homeowner_code <- as.numeric(returns1$homeowner_code)
df=data.frame(returns1$return, returns1$bops, returns1$homeowner_code, returns1$length_of_residence, returns1$child)
cor(df, use="pairwise.complete.obs")[,1:2]
```


```{r echo=FALSE, warning=FALSE, message=FALSE}
## 2SLS with 2 instruments (homeowner_code + length_of_residence)
#sls2 <- ivreg(return ~ bops * store_number + net_purchase_amount + gender + age_band + est_income_code + ethnic_code + month + summary | homeowner_code + length_of_residence + store_number + net_purchase_amount + gender + age_band + est_income_code + ethnic_code + month + summary, data = returns1)
#summary(sls2,diagnostics=TRUE)
```

# Summary
```{r echo=FALSE, warning=FALSE, message=FALSE}
plot(effect(term="bops:store_number", mod=logit1, default.levels=3),multiline=TRUE)
```



